Supplement

### 2023-06-30 writing/supplement.Rmd
update reports
update supplement

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(knitr)
library(here)

@@

# Sensitivity Analyses

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(knitr)
library(here)

@@

# Details on Each Implementation

```{r covidestim-concordance-state, fig.cap="For each implementation, the proportions of simulation intervals where the Covidestim median was below, within, or above the interval are shown, across all states used for the implementation."}

include_graphics(here('figures/concordance-covidestim-state.pdf'))

```{r, fig.cap="The proportions of simulation intervals where the Covidestim median was below, within, or above the intervals are shown, considering all counties except Dukes/Nantucket, where Covidestim estimates were not produced."}

include_graphics(here('figures/concordance-covidestim-county.pdf'))

\newpage

# Full Set of Simulation Intervals by State

```{r sim-intervals-state}

include_graphics(here('figures/intervals-and-covidestim-all-states.pdf'))

## COVID-19 Trends and Impact Survey

# County Results by Implementation
